---
title: Regression Models Project "Motor Trend"
author: 'JHU Data Science'
date: 'By Jean Marie Cimula'
output: html_document
---


###Synopsis

The goal of this paper is to present:  the concept of prediction in  Multiple Regression, the assumptions underlying multiple regression analysis and variable selection.
We want to predict the consumption of cars in the RStudio datasets mtcars containing 32 observations on 11 variables.
```{r}
#mpg: Miles per US gallon
#cyl: Number of cylinders
#disp: Displacement (cubic inches)
#hp: Gross horsepower
#drat: Rear axle ratio
#wt: Weight (lb / 1000)
#qsec: 1 / 4 mile time
#vs: V/S
#am: Transmission (0 = automatic, 1 = manual)
#gear: Number of forward gears
#carb: Number of carburetors
```
```{r}
#Loading libraries
library(ggplot2)
library(MASS)
```

####Exploratory Data Analysis
```{r}
#Dataset
data(mtcars)

#For predicting the consumption, we prefer to three dependent variable(Transmission, Cylinder,Displacement and Weight) and one response variable (Miles per US gallon)

#Linear Model
varReg <- lm(mpg ~ cyl + wt + am + disp,data=mtcars)
summary(varReg)
```

Let remove disp because its p-value
```{r}
#New model : mpg ~ cyl + wt + am 
varLm <- lm(mpg ~ cyl + wt + am,data=mtcars)
summary(varLm)
```

Multiple R-squared and Adjusted R-squared of both models are roughly equals 

```{r}
#Variable selection
stepAIC(varLm, direction="both")$anova
```

We can see above the result of the final model which shows that Cylinder and Weight are the relevant variables to explain car consumption. 

####Appendix

```{r}
#Pair plots of dependent variables of the lm that spawned the final model
data <- mtcars[,c("am","cyl","wt")]
pairs(data)
```
```{r}
#LM Plots
par(mfrow =c(2,2))
plot(varLm)
```
```{r}
#Residuals vs variables
Res <- residuals(varLm)
par(mfrow =c(2,2))
for (j in 1:3){ 
               plot(data[,j],Res, ylab="Residuals", xlab=names(data)[j],col="red")
               abline(h=0)
              }
```
